### 2021-11-11 sections/strategy_Htautau.tex
updating the limit of Wilson coefficients

The analysis strategy adopted in the $\Htautau$ search is similar to the one used in Ref.~\cite{fcnc36,Chen:2015nta} but extended to more signal channels.

@@

The $tt(qH)$ and $tH$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson and the remaining SM $t\to Wb$ decay. There is an additional $q$-jet from the FCNC $t\to qH$ decay in the top pair production. 
%at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon with significant $\met$ is also expected.
In a significant fraction of the events, the smaller jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
resulting in some signal events mixed with production mode having only three reconstructed jets.
In order to optimise the sensitivity of the search, the selected events are categorised into seven SRs based on the number of light lepton and
$\had$ candidates, and on the number of light flavored jets:
$t_l\hadhad$, $t_l\had$-1j, $t_l\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}.

@@

Finally, the four-momenta of the invisible decay products from the decay of di-taus 
are estimated from a kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
measured $\met$ within their expected resolutions. The resolution on the Higgs boson mass is taken to be $20~\gev$, respectively, while the resolution on the measured $\met$ is parameterised as a linear function of 
$\sqrt{\sum E_T}$, where $\sum E_T$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
After the $\chi^2$ minimisation, the Higgs boson four-momentum, and hence its invariant mass, as well as the 
four-momentum of the parent top quarks, are determined with better resolution in the signal events.

@@

The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_tthML} -~\ref{tab:importance_xTFW} and defined in the following:

@@

\item $\Delta R(\tau,qjet)$ is the angular distance between the tau and the reconstructed $q$-jet.

@@

The expected signals (dashed red) are also shown after normalized to the total number of events in the predicted
background for the shape comparison of the distributions.   

>>>>

The analysis strategy adopted in the $\Htautau$ search is similar to the one used in Ref.~\cite{fcnc36,Chen:2015nta} but extended to more search channels.

@@

The $tt(qH)$ and $tH$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson and the remaining SM $t\to Wb$ decay. There is an additional $q$-jet from the FCNC $t\to qH$ decay in the top pair production. 
%at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon with significant $\met$ is also expected.
In a significant fraction of the events, the smaller jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
resulting in some signal events mixed with production mode having only three reconstructed jets.
In order to optimise the sensitivity of the search, the selected events are categorised into seven SRs based on the number of light leptons,
$\had$ candidates, and on the number of light flavored jets:
$t_l\hadhad$, $t_l\had$-1j, $t_l\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}.

@@

Finally, the four-momenta of the invisible decay products from the decay of di-taus 
are estimated using a kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
measured $\met$ within their expected resolutions. The resolution on the Higgs boson mass is taken to be $20~\gev$, respectively, while the resolution on the measured $\met$ is parameterised as a linear function of 
$\sqrt{\sum E_T}$, where $\sum E_T$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
After the $\chi^2$ minimisation, the Higgs boson four-momentum, and hence its invariant mass, as well as the 
four-momentum of the parent top quarks, are determined with better resolution in the signal events.

@@

The BDT input variables in each SR and their importance are listed in Table~\ref{tab:importance_tthML} and~\ref{tab:importance_xTFW} and defined in the following:

@@

\item $\Delta R(\tau,qjet)$ is the angular distance between the tau and the reconstructed $q$-jet. If there are two taus in the event, the leading one is used.

@@

The expected signals (dashed) are also shown after scaled up for the shape comparison of the distributions.
%by a large factor normalized to the total number of events in the predicted
%background for the shape comparison.   

### 2021-11-11 sections/systematic_uncertainties.tex
updating the limit of Wilson coefficients

Another significancant background in hadronic channel stems from the ztautau samples, several sources of uncertainty are considered for these samples: 
the PDF variation considering the standarnd deviation of the 100 NNPDF replicas event weights of NNPDF3.0nnlo PDF set used in Sherpa, renormalisation($\mu_{R}$) and factorisation scales($\mu_{F}$),jet-to-parton matching uncertainty,resummation scale uncertainty, variation in the choice of $\alpha_{S}$, alternative PDF variation evalatued comparing predictions from NNPDF3.0nnlo PDF set (nominal) with MMHT2014nnlo68cl and CT14nnlo PDF sets.

%%Uncertainties affecting the normalisation of the $V$+jets background are estimated for the sum
%%of $W$+jets and $Z$+jets, and separately for $V$+light-jets, $V$+$\geq$1$c$+jets, and $V$+$\geq$1$b$+jets subprocesses.
%%The total normalisation uncertainty of $V$+jets processes is estimated by comparing the data and total background prediction in 
%%the different analysis regions considered, but requiring exactly zero $b$-tagged jets.
%Agreement between data and predicted background 
%in these modified regions, which are dominated by $V$+light-jets, is found to be within approximately 30\%. This bound is taken to 
%be the normalisation uncertainty, correlated across all $V$+jets subprocesses. 
%Since {\sherpa}~2.2 has been found to underestimate $V$+heavy-flavour production by about a factor
%of 1.3~\cite{Aaboud:2017xsd}, additional 30\% normalisation uncertainties are assumed for $V$+$\geq$1$c$+jets and $V$+$\geq$1$b$+jets
%subprocesses, considered uncorrelated between them.

To estimate the uncertainty originating from ISR modelling in the single top samples, the same procedure as $t\bar{t}$ is used. One NP reflects the symmetrised effect of the two shower variations Var3cDown and Var3cUp, and the other NP with name ``scale'' describe the symmetrised effect from the independent variations of the renormalisation and factorisation scale. The impact of the uncertainty from FSR modelling is estimated by reweighting the nominal single top sample. The two variations $\mu^{FSR}_{R} \times 0.5$ and $\mu^{FSR}_{R} \times 2$ are considered.  The standard deviation of 100 NNPDF3.0nnlo variations is calculated Uncertainties on the PDF are evaluated following the recommended prescription in Ref.~\cite{ttRun2}.

The values of the scale-parameters $\mu_{f}$ and $\mu_{f}$ are varied by factors of 2.0 and 0.5 with respect to their default values to obtain the uncertainties related to the renormalization and factorization scales in ttV samples. Uncertainties on the PDF are evaluated following the same procedure in Ref.~\cite{ttZRun2}.

Following the recommendations of the PMG group, the uncertainties to be considered for diboson background include~\cite{dibosonRes} scale variations of the renormalization and factorization scale,
PDF variations and $\alpha_{S}$ variations.

A $+5.8\%-9.2\%$ normalization uncertainty is considered for the ttH background, corresponding to the scale and $\alpha_{S}$ uncertainties in the NLO cross-section computation. A constant PDF uncertainty of $\pm3.6$\% is assumed, as it was done for the previous measurement. Therefore, a overall sytematics with variation 9\% is entered in the final fit model~\cite{ttZRun2}.

%%%Uncertainties affecting the modelling of the single-top-quark background include a 
%%%$+5\%$/$-4\%$ uncertainty of the total cross section estimated as a weighted average 
%%%of the theoretical uncertainties in $t$-, $tW$- and $s$-channel production~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.
%%%Additional uncertainties associated with the modelling of additional radiation are assessed by comparing the nominal
%%%samples with alternative samples where generator parameters are varied.
%%%For the $t$- and $tW$-channel processes, an uncertainty due to the choice of parton shower and hadronisation model is derived 
%%%by comparing events produced by {\powheg} interfaced to {\pythia}~8 or {\herwigpp}.
%%%These uncertainties are treated as fully correlated among single-top-quark production processes, but uncorrelated with the
%%%corresponding uncertainty of the $\ttbar$+jets background.
%%%An additional systematic uncertainty in $tW$-channel production concerning the separation 
%%%between $t\bar{t}$ and $tW$ at NLO is assessed by comparing
%%%the nominal sample, which uses the diagram removal scheme~\cite{Frixione:2008yi}, with an alternative sample
%%%using the diagram subtraction scheme~\cite{Frixione:2008yi}.

%%%%Uncertainties of the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah,Campbell:2011bn},
%%%%as well as an additional 24\% normalisation uncertainty added in quadrature for each additional inclusive jet-multiplicity bin, based on a 
%%%%comparison among different algorithms for merging LO matrix elements and parton showers~\cite{Alwall:2007fs}
%%%%(it is assumed that two jets originate from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
%%%%Therefore, the total normalisation uncertainty is $5\% \oplus \sqrt{N-2}\times 24\%$, where $N$ is the selected jet multiplicity,  
%%%%resulting in 34\%, 42\%, and 48\%, for events with exactly 4 jets, exactly 5 jets, and $\geq$6 jets, respectively. 
%%%%Recent comparisons between data and {\sherpa}~2.1.1 for $WZ(\to \ell\nu\ell\ell) + \geq$4 jets show
%%%%agreement within the experimental uncertainty of approximately 40\%~\cite{Aaboud:2016yus}, which further justifies the above uncertainty.
%%%%Given the very small contribution of this background to the total prediction, the final result is not affected by the assumed modelling
%%%%uncertainties.
%%%%
%%%%Uncertainties of the $\ttbar V$ and $\ttbar H$ cross sections are 15\% and $+10\%$/$-13\%$, respectively,
%%%%from the uncertainties of their respective NLO theoretical cross sections~\cite{Campbell:2012dh,Garzelli:2012bn,deFlorian:2016spz}.

>>>>

Another significancant background in hadronic channel stems from the $Z\rightarrow \tau\tau$ samples, several sources of uncertainty are
considered for these samples: the PDF variation considering the standarnd deviation of the 100 NNPDF replicas event weights of NNPDF3.0nnlo PDF
set used in Sherpa, renormalisation($\mu_{R}$) and factorisation scales($\mu_{F}$),jet-to-parton matching uncertainty,resummation scale uncertainty,
variation in the choice of $\alpha_{S}$, alternative PDF variation evalatued comparing predictions from NNPDF3.0nnlo PDF set (nominal)
with MMHT2014nnlo68cl and CT14nnlo PDF sets.

Uncertainties affecting the normalisation of the $V$+jets background are estimated separately for $V$+light-jets, $V$+$\geq$1$c$+jets,
and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated within approximately 30\% by comparing the
data and total background prediction in the different analysis regions considered, but requiring exactly zero $b$-tagged jets.
%Agreement between data and predicted background 
%in these modified regions, which are dominated by $V$+light-jets, is found to be within approximately 30\%. This bound is taken to 
%be the normalisation uncertainty, correlated across all $V$+jets subprocesses. 
%Since {\sherpa}~2.2 has been found to underestimate $V$+heavy-flavour production by about a factor
%of 1.3~\cite{Aaboud:2017xsd}, additional 30\% normalisation uncertainties are assumed for $V$+$\geq$1$c$+jets and $V$+$\geq$1$b$+jets
%subprocesses, considered uncorrelated between them.

%To estimate the uncertainty originating from ISR modelling in the single top samples, the same procedure as $t\bar{t}$ is used. One NP reflects the symmetrised effect of the two shower variations Var3cDown and Var3cUp, and the other NP with name ``scale'' describe the symmetrised effect from the independent variations of the renormalisation and factorisation scale. The impact of the uncertainty from FSR modelling is estimated by reweighting the nominal single top sample. The two variations $\mu^{FSR}_{R} \times 0.5$ and $\mu^{FSR}_{R} \times 2$ are considered.  The standard deviation of 100 NNPDF3.0nnlo variations is calculated Uncertainties on the PDF are evaluated following the recommended prescription in Ref.~\cite{ttRun2}.

%The values of the scale-parameters $\mu_{f}$ and $\mu_{f}$ are varied by factors of 2.0 and 0.5 with respect to their default values to obtain the uncertainties related to the renormalization and factorization scales in ttV samples. Uncertainties on the PDF are evaluated following the same procedure in Ref.~\cite{ttZRun2}.

%Following the recommendations of the PMG group, the uncertainties to be considered for diboson background include~\cite{dibosonRes} scale variations of the renormalization and factorization scale,
%PDF variations and $\alpha_{S}$ variations.

%A $+5.8\%-9.2\%$ normalization uncertainty is considered for the ttH background, corresponding to the scale and $\alpha_{S}$ uncertainties in the NLO cross-section computation. A constant PDF uncertainty of $\pm3.6$\% is assumed, as it was done for the previous measurement. Therefore, a overall sytematics with variation 9\% is entered in the final fit model~\cite{ttZRun2}.

Uncertainties affecting the modelling of the single-top-quark background include a 
$+5\%$/$-4\%$ uncertainty of the total cross section estimated as a weighted average 
of the theoretical uncertainties in $t$-, $tW$- and $s$-channel production~\cite{Kidonakis:2011wy,Kidonakis:2010ux,Kidonakis:2010tc}.
Additional uncertainties associated with the parton shower, hadronisation and ISR/FSR radiations are also considered using the same procedure
as in $t\bar t$.
%by comparing the nominal
%%%samples with alternative samples where generator parameters are varied.
%%%For the $t$- and $tW$-channel processes, an uncertainty due to the choice of parton shower and hadronisation model is derived 
%%%by comparing events produced by {\powheg} interfaced to {\pythia}~8 or {\herwigpp}.
%%%These uncertainties are treated as fully correlated among single-top-quark production processes, but uncorrelated with the
%%%corresponding uncertainty of the $\ttbar$+jets background.
%%%An additional systematic uncertainty in $tW$-channel production concerning the separation 
%%%between $t\bar{t}$ and $tW$ at NLO is assessed by comparing
%%%the nominal sample, which uses the diagram removal scheme~\cite{Frixione:2008yi}, with an alternative sample
%%%using the diagram subtraction scheme~\cite{Frixione:2008yi}.

Uncertainties of the diboson background normalisation include 5\% from the NLO theory cross sections~\cite{Campbell:1999ah,Campbell:2011bn},
as well as an additional 24\% normalisation uncertainty added in quadrature for each additional inclusive jet-multiplicity bin, based on a 
comparison among different algorithms for merging LO matrix elements and parton showers~\cite{Alwall:2007fs}.
%%%%(it is assumed that two jets originate from the $W/Z$ decay, as in $WW/WZ \to \ell \nu jj$). 
%%%%Therefore, the total normalisation uncertainty is $5\% \oplus \sqrt{N-2}\times 24\%$, where $N$ is the selected jet multiplicity,  
%%%%resulting in 34\%, 42\%, and 48\%, for events with exactly 4 jets, exactly 5 jets, and $\geq$6 jets, respectively. 
%%%%Recent comparisons between data and {\sherpa}~2.1.1 for $WZ(\to \ell\nu\ell\ell) + \geq$4 jets show
%%%%agreement within the experimental uncertainty of approximately 40\%~\cite{Aaboud:2016yus}, which further justifies the above uncertainty.
%%%%Given the very small contribution of this background to the total prediction, the final result is not affected by the assumed modelling
%%%%uncertainties.
%%%%
Uncertainties of the $\ttbar V$ and $\ttbar H$ cross sections are 15\% and $+10\%$/$-13\%$, respectively,
from the uncertainties of their respective NLO theoretical cross sections~\cite{Campbell:2012dh,Garzelli:2012bn,deFlorian:2016spz}.
